\mytitle

### 2012-02-23 papers/SAS2012/implicitization.tex
URL de PAGAI + citation rapport M2

We have implemented our proposed solutions inside a prototype of intraprocedural
static analyzer called PAGAI,
as well as the classical abstract interpretation algorithm, and the state-of-the-art
techniques \emph{Path Focusing} \cite{Monniaux_Gonnord_SAS11} and \emph{Guided
Static Analysis} \cite{DBLP:conf/sas/GopanR07}.

>>>>

We have implemented our proposed solutions inside a prototype of intraprocedural
static analyzer called PAGAI,
as well as the classical abstract interpretation algorithm, and the state-of-the-art
techniques \emph{Path Focusing} \cite{Monniaux_Gonnord_SAS11} and \emph{Guided
Static Analysis} \cite{DBLP:conf/sas/GopanR07}. It is
available online at \url{https://forge.imag.fr/projects/pagai/}. The
implementation is documented in~\cite{julien-henry-m2r}.
\MM{pas idéal de citer un rapport de M2, mais ça a des chances de
  faire taire les reviewers qui voudraient des détails sur comment
  c'est fait, et on n'a pas la place de mettre plus. Le
  paragraphe~\ref{sec:analysis-algorithm} a été supprimé depuis
  PLDI ...}
